SIMD\slash SIMT-vectorized Thermo-chemical Source Term Evaluation

### 2018-02-14 paper.tex
goals

This work will study the performance of thermo-chemical source term evaluation of automatically generated shallow-SIMD vectorized codes for a wide range chemical kinetic models on the CPU.
The performance will be compared to a baseline shallow-SIMT vectorized code to determine the effective SIMD speedup.
Finally future extensions to this work will be detailed.

>>>>

This work will build upon our previous analytical chemical kinetic Jacobian code,~\cite{Niemeyer:2016aa} in order to:
\begin{itemize}
 \item Derive and validate a new Jacobian formulation that greatly increases sparsity
 \item Enable cross-platform SIMD\slash SIMT vectorization for the CPU, GPU and other accelerators
 \item Investigate the performance for a wide range chemical kinetic models, specifically looking at speedups due to SIMD\slash SIMT-vectorization as well as relative to the previous version of \texttt{pyJac}, and finally
 \item Discuss future extensions to this work as well as the most promising directions for SIMD\slash SIMT vectorization in reactive flow simulations
\end{itemize}
.
